---
title: "Fantasy Football Research"
author: "John Miller"
date: "August 5th, 2022"
output: html_notebook
  
---
## About This
 This is a simple statistical analysis and plotting of fantasy football data from the 2021-2022 season. The goal of this is to refresh myself on R before the semester, and primarily to see if there are any trends that I can use to potentially find a good pick for my upcoming fantasy draft. The data is based off of a PPR (Points Per Reception) league.


### Packages and Clean Up

```{r}
# clean up workspace enivronment
rm(list = ls())

# Load Packages
library(mosaic)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(readr)
library(rvest)


```

### Loading in the Data Source

I am using data from ProFootballReference.com, which had their data provided to them by SportRadar.
```{r}
web_page <- "https://www.pro-football-reference.com/years/2021/fantasy.htm#fantasy::27"
Tables <- web_page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
FF2021 <- Tables[[1]] 
  names(FF2021) <- NULL
  FF2021



```



