---
title: "Fantasy Football Research"
author: "John Miller"
date: "August 5th, 2022"
output: html_notebook
  
---
## About This
 This is a simple statistical analysis and plotting of fantasy football data from the 2021-2022 season. The goal of this is to refresh myself on R before the semester, and primarily to see if there are any trends that I can use to potentially find a good pick for my upcoming fantasy draft. The data is based off of a PPR (Points Per Reception) league.


### Packages and Clean Up

```{r}
# clean up workspace enivronment
rm(list = ls())

# Load Packages
library(mosaic)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(readr)
library(rvest)
library(dplyr)


```

### Loading in the Data Source and Cleaning it

I am using data from ProFootballReference.com, which had their data provided to them by SportRadar.
Note: After figuring out how to get the first row as the header and variable names, I then realized some of the variables had duplicated names (ex. TD being the name of 2 separate columns). I solved this by downloading the janitor package and then naming the data frame after using the janitor package, and it was solved. The last thing I needed to do was rename the variables to make it clear that td_2 actually meant rushing touchdowns.
```{r}
## Cleaned up Data Table, not sure if there was an easier way to do this
web_page <- "https://www.pro-football-reference.com/years/2021/fantasy.htm#fantasy::27"
Tables <- web_page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)
FF2021 <- Tables[[1]] 
names(FF2021) <- NULL
colnames(FF2021) <- FF2021[1,] 
FF2021Fixed <- FF2021[-c(1),]
FF2021Fixed <- janitor::clean_names(FF2021Fixed)

```


```{r}
## Renaming variables for clarity
## NOTE: Can only run once then get error message 
FF2021Fixed <- FF2021Fixed %>%
  rename("passing att" = "att") %>%
  rename("passing yds" = "yds") %>%
  rename("passing td" = "td") %>%
  rename("rushing att" ="att_2")
  rename("rushing td" = "td_2") %>%
  rename("rushing yds" = "yds_2") %>%
  rename("receiving yds" = "yds_3") %>%
  rename("receiving td" = "td_3") %>%
  rename("total td" = "td_4")



  



```


## Inspecting the Table



```{r}
  View(FF2021Fixed)
```

```{r}




```



